% LaTeX file for resume 
% This file uses the resume document class (res.cls)
\documentclass[12pt]{res} 
\usepackage[usenames, dvipsnames]{color}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
\usepackage{newcent}   % uses new century schoolbook postscript font 
\newsectionwidth{8pt}  % So the text is not indented under section headings
\setlength{\textheight}{10.2in} % set text height big enough for box
\topmargin=-18mm       % to start box .5in from top of page
\oddsidemargin=-20mm   % to start box .5in from left of page
\renewcommand{\baselinestretch}{1.05}
\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% The following lines define \boxaround, used to draw a box on the page.
% The parameter is the entire text of the resume. Must fit on one page!
%
% \boxaroundhmargin is the left & right margin around the text inside the box.
% \boxaroundvmargin is the top & bottom margin around the text inside the box.
% \boxrulethickness controls thickness of line used to draw the box.
% You can change these 3 things in the lines below:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newdimen\boxrulethickness\newdimen\boxaroundhmargin\newdimen\boxaroundvmargin
\boxrulethickness=0pt        %controls thickness of line 
\boxaroundhmargin=1pt        % about a half inch
\boxaroundvmargin=1pt        % to fit more text on page, make this smaller
%%%%%%%%%%%%%%%%%%%%%%%%% Don't read this stuff %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\hsize=7.86in \vsize=12in             % use bigger dimensions for box
\newbox\MACboxA  \newdimen\MACdimenA
% \borderandboxit is used inside \boxaround:
\def\borderandboxit#1#2#3{\vbox{\hrule height#2\hbox{\vrule width#2\hskip#1\hskip-#2%
  \vbox{\vskip#1\relax#3\vskip#1}\hskip#1\hskip-#2\vrule width#2}\hrule height#2}}
%
\long\def\boxaround#1{\vskip6pt
  {\MACdimenA=\hsize \advance\MACdimenA by-\boxaroundhmargin
   \advance\MACdimenA by-\boxaroundhmargin   % once for each side
   \setbox\MACboxA=\hbox to \hsize{\hskip\boxaroundhmargin%\hss
                     \vbox{\hsize=\MACdimenA
                           \vskip\boxaroundvmargin #1
                           \vskip\boxaroundvmargin}\hss}%
   \borderandboxit{0pt}\boxrulethickness{\box\MACboxA}}%
  \vskip2pt plus0pt minus0pt
}
%%%%%%%%%%%%%%%%%%%  End of \boxaround macro %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\boxaround{ % put the text on the page inside a box  
\begin{resume}
\begin{list}{}{\leftmargin=1em}
\item \centering {\textbf{Steven Ellis}}
\item
\item{\textit{Education}
\begin{list}{}{\leftmargin=1em}
\item Brown University \dotfill A.B. 2011
\item Applied Psychology\dotfill\textit{magna cum laude}
\end{list}}
\item{\textit{Experience}
\begin{list}{}{\leftmargin=1em}
\item Executive Office of The President of the United States\dotfill Data Scientist\dotfill1/2023 -- 6/2023
\begin{list}{-}{\leftmargin=1em}
\item Tour of duty with the United States Digital Service, the White House's in-house tech team.
\item Produced the first comprehensive analysis of federal funding for Puerto Rico.
\end{list}
\item GoBuild (defunct)\dotfill Second Employee \dotfill7/2020 -- 6/2021
\begin{list}{-}{\leftmargin=1em}
\item Ideated and developed pre-seed startup's product, an AI/ML (R, XGBoost) tool which estimated effect of renovations on sales price.
\item Led acquisition of home purchase data, computer vision API, and other miscellaneous datasets.
\item Contributed to successful YCombinator application and subsequent funding round.
\end{list}
\item Divvy Homes\dotfill Head of Data Science \dotfill9/2018 -- 6/2020
\begin{list}{-}{\leftmargin=1em}
\item Developed Series A/B startup's first home pricing and credit AI/ML (R, ensemble XGBoost / KNN) services.
\item Developed AI/ML service APIs, monitoring, and error-handling (R, Python), deployed to production (Github, Heroku).
\item Developed and implemented policies to re-balance riskiness of home and tenant portfolio.
\item Hired and managed two data scientists, roadmapped and directed projects.
\item Engaged with equity and debt investors before, during, and after successful funding round.
\item Led acquisition of home purchase data.
\end{list}
\item Uber Technologies\dotfill Data Scientist \dotfill5/2014 -- 12/2016
\begin{list}{-}{\leftmargin=1em}
\item Sixth data scientist, served as company-wide experimentation expert, wrote guide to mobile experimentation.
\item Introduced variance reduction to marketplace experimentation (R, Python, ensemble Random Forest / high-dimensional matching), pioneering causal inference methods at Uber.
\item Launch member of Uber API, quantified value of partnerships using Random Forest (Python).
\item Launch member of experimentation platform ("Morpheus"), identified and analyzed root-cause of hazardous flaws in tool.
\end{list}
\item Google (now Alphabet)\dotfill Quantitative User Experience Researcher\dotfill4/2011 -- 4/2014
\begin{list}{-}{\leftmargin=1em}
\item Guided Google Fiber rollout using high-dimensional matching (R) -\\ https://research.google/pubs/pub41379/.
\item Built interactive, live choropleth to track Google Fiber rollout.
\item Guided Google Fiber SMB pricing using Choice-Based Conjoint analysis (R) -\\ https://research.google/pubs/pub41381/.
\item Mined ad data to guide Google Identity Platform partnerships team (R, Python, Dremel).
\item Directed in-person research and followed up with production experiments on Single Sign-On product.
\end{list}
\end{list}}
\item
\end{list}
\end{resume}
} %    end the material being boxed.
\end{document}